### 2024-05-30 README.Rmd
README updates

# Fit the model
fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married +
                                     nodegree + re74 + re75),
           data = lalonde, family = binomial)
```

Next, to estimate the ATT risk ratio, we simulate coefficients from their implied distribution and compute the effects of interest in each simulation, yielding a distribution of estimates that was can summarize and use for inference:

@@

Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters. The delta method involves multiple assumptions: 1) the model coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance. When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate. Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference (though other assumptions are required); however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.

Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3) (though it still relies on the central limit theorem to assume the coefficients are normally distributed), and it is faster and more stable than bootstrapping because the model only needs to be fit once. Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution. Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals. Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory Wald confidence intervals and p-values can be computed. The methodology of simulation-based inference is explained in King, Tomz, and Wittenberg (2000).

@@

There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions. `clarify` also offers support for models fit to multiply imputed data with the `misim()` function.

>>>>

# Fit the model
fit <- glm(I(re78 > 0) ~ treat + age + educ + race + married +
             nodegree + re74 + re75,
           data = lalonde, family = binomial)
```

Next, to estimate the ATT risk ratio, we simulate coefficients from their implied distribution and compute the effects of interest in each simulation, yielding a distribution of estimates that we can summarize and use for inference:

@@

Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters. It involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution. Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals. Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory Wald confidence intervals and p-values can be computed. The methodology of simulation-based inference is explained in King, Tomz, and Wittenberg (2000).

@@

There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::avg_predictions()` and `marginaleffects::avg_slopes()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions. `clarify` also offers support for models fit to multiply imputed data with the `misim()` function.
